% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% -*- coding: UTF-8; -*-
% vim: set fenc=utf-8

% See "README.md" for instructions on compiling this document.

\documentclass[letterpaper,MMMyyyy,nonstopmode]{simpleresumecv}
% Class options:
% a4paper, letterpaper, nonstopmode, draftmode
% MMMyyyy, ddMMMyyyy, MMMMyyyy, ddMMMMyyyy, yyyyMMdd, yyyyMM, yyyy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% PREAMBLE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% CV Info.
\newcommand{\CVAuthor}{Praveen Kumar}
\newcommand{\CVTitle}{Praveen Kumar's CV}
\newcommand{\CVNote}{CV compiled on {\today}}
\newcommand{\CVWebpage}{https://fedoraproject.org/wiki/User:Kumarpraveen}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={XeLaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=OneColumn,
pdfpagemode=UseOutlines,
hidelinks,
breaklinks}

% Shorthand.
\newcommand{\Code}[1]{\mbox{\textbf{#1}}}
\newcommand{\CodeCommand}[1]{\mbox{\textbf{\textbackslash{#1}}}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% ACTUAL DOCUMENT.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%
% TITLE BLOCK %
%%%%%%%%%%%%%%%

\Title{\CVAuthor}

\begin{SubTitle}
\href{https://www.google.com/maps/place/Pune+India}
{DSK Sunderban, Amanora, Pune 411028, India}
\par
\href{mailto:kumarpraveen.nitdgp@gmail.com}
{kumarpraveen.nitdgp@gmail.com}
\,\SubBulletSymbol\,
+91\,7276249468
\,\SubBulletSymbol\,
\href{\CVWebpage}
{\url{\CVWebpage}}
\end{SubTitle}

\begin{Body}

%%%%%%%%%%%%%
%% Profile %%
%%%%%%%%%%%%%
\Section
{profile}
{profile}
{PDF:profile}

\Entry
\begin{Detail}
I am an experienced developer, looking for new exciting challenges. I have worked on various Linux products and projects over the past 7 years on different levels. I am eager to learn new technologies and a quick-learner.
\end{Detail}

%%%%%%%%%%%%%%%
%% EDUCATION %%
%%%%%%%%%%%%%%%

\Section
{Education}
{Education}
{PDF:Education}

\Entry
\href{https://www.nitdgp.ac.in/}
{\textbf{National Institute of Technology}},
Durgapur, West Bengal, India

\Gap
\BulletItem
B.Tech in Information Technology
\href{https://www.nitdgp.ac.in/department/CS}
{Information Technology}
\hfill
\DatestampYMD{2007}{07}{15} --
\DatestampYMD{2011}{06}{15}
\begin{Detail}
\SubBulletItem
Thesis:
\href{https://bitbucket.org/kumarpraveen/lsync}
{A file synchronizer for Linux.}
\SubBulletItem
Adviser:
\href{https://www.nitdgp.ac.in/faculty/fcb853d8-bbdb-4327-a31f-1eda672da992}
{Ass. Prof.~Animesh~Dutta}
\SubBulletItem
Focus:
Networking, database, Application development
\SubBulletItem
Cumulative GPA: 8.4 / 10.0
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Work Experience: %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Work Experience}
{Work Experience}
{PDF:Work Experience}

\Entry
\href{https://redhat.com}
{\textbf{Red Hat }}
\hfill
\DatestampY{2013} --
Present

\BulletItem
\href{https://github.com/code-ready/crc}
{{CodeReady Container}}, a tool that helps to run OpenShift-4.x locally by running a single-node \newline OpenShift cluster inside a VM (Platform independent)
\hfill
\DatestampY{2018} --
present

\BulletItem
\href{https://github.com/minishift/minishift}
{{Minishift}}, a tool that helps to run OpenShift-3.x locally by running a single-node \newline OpenShift cluster inside a VM (Platform independent)
\hfill
\DatestampY{2017} --
2018

\BulletItem
\href{https://github.com/projectatomic/adb-atomic-developer-bundle}
{{Atomic Developer Bundle}},  a prepackaged development environment filled with \newline production-grade, pre-configured tools, that makes container developers' lives easier.
\hfill
\DatestampY{2016} --
2017

\BulletItem
Third party vendor software and plugin certification and evaluation process for \newline RHEL OpenStack's Object storage (swift).
\hfill
\DatestampY{2015} --
2016

\BulletItem
CI/CD, Enabled team to use CI/CD methodology across the projects and defined \newline e2e pipelines. Used Ansible and Jenkins Job Builder to provide infra as code solution.
\hfill
\DatestampY{2013} --
2014

\Gap
\Gap
\Gap
\Entry
\href{https://www.hpe.com}
{\textbf{Hewlett Packard Enterprise}}
\hfill
\DatestampY{2011} --
2013

\BulletItem
Automation of \href{https://www.hpe.com/us/en/product-catalog/detail/pip.5182020.html}{HPE Smart Update Manager} Installation guide.
\hfill
\DatestampY{2011} --
2013

%%%%%%%%%%%%
%% SKILLS %%
%%%%%%%%%%%%

\Section
{Skills}
{Skills}
{PDF:Skills}

\Entry
golang,
python,
Containers,
Continue Integration,
Linux,
Virtualization

%%%%%%%%%%%%%%%%%%%%%%%
%% CAMPUS ACTIVITIES %%
%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Campus Activities}
{Campus Activities}
{PDF:CampusActivities}

\Entry
\href{http://nitdgplug.org/}
{\textbf{Volunteer to Linux User Group}},
NIT Durgapur

\Gap
\BulletItem
Vice President
\hfill
\DatestampYMD{2010}{06}{15} --
\DatestampYMD{2011}{02}{20}
\begin{Detail}
\SubBulletItem
Spread awareness about Open Source Software.
\SubBulletItem
Conducting workshop and Talks on different topics around Linux
\SubBulletItem
Part of organization committee for Mukti (Open-Source Techfest)
\end{Detail}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Other Projects/Achievements: %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\Section
{Other Work\newline
Experience}
{Other Work Experience}
{PDF:OtherWorkExperience}

\Entry
\href{https://getfedora.org/}
{\textbf{Fedora Community}},
Remote

\Gap
\BulletItem
Package Maintainer
\hfill
\DatestampYMD{2010}{8}{8} --
present
\begin{Detail}
\SubBulletItem
Maintain around 35 rpm packages for Fedora offical repo.
\SubBulletItem
Reviewed packages on Fedora Bugzilla.
\SubBulletItem
https://src.fedoraproject.org/user/kumarpraveen/projects
\end{Detail}

%%%%%%%%%%%%%%%
%% LANGUAGES %%
%%%%%%%%%%%%%%%

\Section
{Languages}
{Languages}
{PDF:Languages}

\BulletItem
Hindi: Native language.

\Gap
\BulletItem
English: Fluent (speaking, reading, writing).

%%%%%%%%%%%%%%%
%% INTERESTS %%
%%%%%%%%%%%%%%%

\Section
{Interests}
{Interests}
{PDF:Interests}

\Entry
Running,
Cycling.

%%%%%%%%%%%%%%%%
%% REFERENCES %%
%%%%%%%%%%%%%%%%

\Section
{References}
{References}
{PDF:References}

\BulletItem
\textbf{Professor Animesh Dutta}
\newline
Asst. Professor of Computer Science and Engineering
\newline
National Institute of Durgapur
\newline
West Bengal, India
\newline
\href{mailto:animeshrec@gmail.com}
{animeshrec@gmail.com}
\,\SubBulletSymbol\,
+91\,94743-64241

%%%%%%%%%%%
% CV NOTE %
%%%%%%%%%%%

\UseNoteFont%
\null\hfill%
[\textit{\CVNote}]
\end{Body}
\end{document}
